From Reversible Programs to \\ Univalent Universes and Back

### 2017-07-03 upi.tex
fix typo

We add a new level to $\{\PiTwo\}$ to prove the full correspondence of the first 2-levels of $\{\PiTwo\}$ and $\{\bt\}$:
\[\def\arraystretch{0.8}\begin{array}{l@{\quad}rclrl}
(\textit{3-combinators}) & \xi &::=& \trunc &:& \alpha \isothree \alpha
\end{array}\]

\begin{theorem}[Soundness and completeness for $\{\PiTwo\}$]
  There exist functions $\dbracket{ \_ }_n$ which map $n-$combinator in $\PiTwo$ to $n-$path in $\{\bt\}$,
  such that for all $n-$combinators $p, q$, $p \leftrightarrow_n q$ iff $\dbracket{ p }_n = \dbracket{ q }_n$.
\end{theorem}

>>>>

We add a new level to $\PiTwo$ to prove the full correspondence of the first 2-levels of $\PiTwo$ and $\{\bt\}$:
\[\def\arraystretch{0.8}\begin{array}{l@{\quad}rclrl}
(\textit{3-combinators}) & \xi &::=& \trunc &:& \alpha \isothree \alpha
\end{array}\]

\begin{theorem}[Soundness and completeness for $\PiTwo$]
  There exist functions $\dbracket{ \_ }_n$ which map $n-$combinator in $\PiTwo$ to $n-$path in $\{\bt\}$,
  such that for all $n-$combinators $p, q$, $p \leftrightarrow_n q$ iff $\dbracket{ p }_n = \dbracket{ q }_n$.
\end{theorem}
